Predicting the 2024 US Presidential Election with a Model-Based Forecast

### 2024-11-04 paper/paper.qmd
fix git

# Create a bar chart for the distribution of numeric_grade
p1 <- ggplot(cleaned_data, aes(x = numeric_grade)) +
  geom_bar(fill = "steelblue", color = "black") +
  labs(title = "Distribution of Polling Scores",
       x = "Numeric Grade",
       y = "Count") +
  theme_minimal()

# Create a bar chart for the distribution of transparency_score
p2 <- ggplot(cleaned_data, aes(x = transparency_score)) +
  geom_bar(fill = "darkorange", color = "black") +
  labs(title = "Distribution of Transparency Scores",
       x = "Transparency Score",
       y = "Count") +
  theme_minimal()

>>>>

# Create a bar chart for the distribution of numeric_grade
p1 <- ggplot(cleaned_data, aes(x = numeric_grade)) +
  geom_bar(fill = "steelblue", color = "black") +
  labs(x = "Numeric Grade",
       y = "Count") +
  theme_minimal()

# Create a bar chart for the distribution of transparency_score
p2 <- ggplot(cleaned_data, aes(x = transparency_score)) +
  geom_bar(fill = "darkorange", color = "black") +
  labs(x = "Transparency Score",
       y = "Count") +
  theme_minimal()
